Interactive Tools for Science Advice

### 2019-11-03 analysis/presentation/interactive_tools.Rmd
Draft seminar presentation up to tagging data section

@@

```{r, out.width = "100%"}
knitr::include_graphics("figures/canada_poll_tracker.PNG")
```

@@

- Here we aim to demonstrate that interactive tools simplify our workflow, from data and model exploration to communication

>>>>

<style>
@import url('https://fonts.googleapis.com/css?family=Montserrat');
</style>

@@

```{r, out.width = "100%"}
# knitr::include_graphics("figures/canada_poll_tracker.PNG")
knitr::include_url("https://newsinteractives.cbc.ca/elections/poll-tracker/canada/", height = "300px")
```

@@

- Using examples we aim to demonstrate that interactive tools can simplify our workflow, from data and model exploration to communication
<br>
- Examples:
    1. **RStrap Explorer:** A tool for examinging fishery-independent survey data
    2. **Tag Explorer:** A mapping tool developed for the exploration of a long-term tagging study
    3. **NCAM Explorer:** A tool for exploring results from the Northern Cod Assessment Model

## RStrap Explorer

<div style="float: left; width: 50%;">

- Fisheries-independent surveys have become a mainstay in stock assessment
- Stratified-random surveys have been conducted by DFO for > 40 years
- Typically analyzed using stratified analyses (RStrap in NL region)

<div style="float: right; width: 45%; padding-left: 5%">

<br>
<img src="figures/teleost_twitter_crop.jpg" width="100%"/>
<font size="1"> 
<br>
&nbsp; <a href="https://twitter.com/coastguardcan/status/879410397790515201">Canadian Coast Guard | Twitter</a>
</font>

## RStrap Explorer {.smaller}

> - Running a series of stratified analysis can be cumbersome

```{r, eval = FALSE, echo = TRUE}

library(Rstrap)

## Load survey data
load("converted_set_details_2017-04-27.Rdata")
load("converted_length-frequency_data_2017-04-27.Rdata")
load("age-growth_data_2017-04-27.Rdata")

## 3NO Witch Flounder
witch <- strat.fun(setdet = setdet, data.series = "Campelen", 
                   species = 890, survey.year = 1995:2012, 
                   season = "spring", NAFOdiv = c("3N", "3O"))

## 3K Roughhead Grenadier (length disaggregated)
grenadier <- strat.fun(setdet = setdet, lf = lf, data.series = "Campelen", 
                       program = "strat2 & strat1", species = 474, survey.year = 2012, 
                       season = "fall", NAFOdiv = "3K", strat = 622:654, sex = "unsexed", 
                       length.group = 0.5, group.by = "length")

## 2J3KL Greenland Halibut (length and age disaggregated)
turbot <- strat.fun(setdet = setdet, lf = lf, ag = ag, data.series = "Campelen", 
                    program = "strat2 & strat1", species = 892, survey.year = 1998:2012, 
                    season = "fall", NAFOdiv = c("2J", "3K", "3L"), 
                    sex = c("male","female","unsexed"), length.group = 1, 
                    group.by = "length & age")

## 3Ps Atlantic Cod (length and age disaggregated)
cod <- strat.fun(setdet = setdet, lf = lf, ag = ag, data.series = "Campelen", 
                 program = "strat2 & strat1", species = 438, survey.year = 1998:2012, 
                 season = "spring", NAFOdiv = "3P", sex = c("male","female","unsexed"), 
                 length.group = 1, group.by = "length & age")

- This doesn't include code for plotting these results

## RStrap Explorer

- A dashboard was created using the **`shiny`**, **`flexdashboard`**, **`plotly`**, and **`crosstalk`** packages to dynamically run and explore RStrap results
- Four primary pages:
    1. **Survey Indices** contains stock level estimates of biomass and abundance
    2. **Age & Length Distributions** contains length and age frequency plots 
    3. **Recruitment** displays recruitment indices
    4. **Help** provides additional context to the survey data and analysis

## RStrap Explorer {data-background="figures/RStrap_dashboard_biomass.png" data-background-position="center bottom"}

## RStrap Explorer {data-background="figures/RStrap_dashboard_freq.png" data-background-position="center bottom"}

## Tag Explorer

- For some data-rich stocks, mark and recapture studies are carried out to estimate movement, growth rate, natural mortality, etc.
- There is a long-standing tagging program for Northern cod
    - \>60 years, >60,000 records, 1,000 - 10,000 tags deployed annually

<img src="figures/cod_tagging.jpg" width="100%"/>
<font size="1"> 
Photo: John Brattey 
</font>

## Tag Explorer

> - Spatial explorations of these data have been limited since the seminal work by Taggart et al. 1995

<div style="float: left; width: 25.6%; padding: 1%">
<div class="drop-shadow" style="background-color: rgb(236, 192, 107);">
<img src="figures/taggart_1.png" width="100%"/>
</div>
</div>

<div style="float: left; width: 26.4%; padding: 1%">

<div class="drop-shadow">
<img src="figures/taggart_2.png" width="100%"/>
</div>

<div style="float: left; width: 42%; padding: 1%">

<div class="drop-shadow">
<img src="figures/taggart_3.png" width="100%"/>
</div>

- **Nearly 500 pages!**

## Tag Explorer

- A dashboard was created using the **`shiny`**, **`shinydashboard`**, and **`leaflet`** packages to dynamically explore this large dataset
- Contains
    - One primary page, **Main map**, where release and recovery locations are mapped
    - A series of summary pages where these data are summarised

## Tag Explorer {data-background="figures/tagging_dashboard_map_tab.png" data-background-position="center bottom"}

## Tag Explorer {data-background="figures/tagging_dashboard_summary_tab.png" data-background-position="center bottom"}
